\TheTitle

### 2017-07-12 paper/study.tex
Study procedure
Include the study procedure in the paper.
This is high-level, the depth is in the subsections for the task groups.

Each task group is applied to both commits, with the order of the commits
randomized between participants to mitigate the effects of order-bias.

The conceptual tasks are the second part of the study. These tasks start
with the participant taking 10 minutes to draw a diagram showing how one
of the commits

@@

\textbf{Procedure}

\dmg{tell me first why you need to create a script, so I know what you
  do something: we did random assignment of tasks (explain what you did)
  and randomized the order in which the tasks were performed.  Then
  explain why you need a script}

\dmg{it does not randomize the order the tools. It randomizes which tool
  is going to be used on each tasks.  be precise with your language}

\dmg{what you explained how commits relate to tasks and how they get
  assigned? think as if you are explaining this to somebody who has to
  do this: you are the designer, explaining the why and the how }

For each participant, we run a simple python script to generate the
script for the study, eliminating the possibility of bias from us. The
script randomizes the order of the tools, the order of the commits, the
order of the task sets, and the order of the tasks within each task set,
where appropriate.

>>>>

The conceptual tasks follow the introduction, followed by the
summarization, which are then followed by the user opinion. The study is
completed with three questions to enable us to know more about the
participants;

\begin{itemize}
  \item How long have you used git?
  \item For what kind of projects have you used git?
  \item How many commits, files, and collaborators were involved with
    the largest repository you have worked with?
\end{itemize}

To mitigate the order bias cased by using one tool before the other or
one commit before the other, we randomize both the tool and commit
between participants. The conceptual tasks are run twice, once with
\comA and once with \comB, in the same order for all participants using
the git tools.

\evan{This paragraph is kind of tricky to explain well. See if you can
  understand what I'm trying to say} The summarization tasks are run
four times, once with \comA and \tool, \comB and \tool, \comA and git
tools, and \comB and git tools. The participant will start with one
tool, and complete the tasks for both commits in that tool. The order of
the commits is the same as in the conceptual tasks. Once they complete
the summarization tasks for both \comA and \comB, they will switch to
the other tool and complete the tasks again on the commits in the same
order. The order of the tasks is consistent for all four runs.

The user opinions do not directly involve working with the tools or the
commits, so the ordering of the tools

@@

We use a script written in python 3.6.1 in order to assure that we do no
bias the randomization, and ensure that correct ordering is maintained
between tools, tasks, and commits. The script produces the entire script
for the study, so we only need to read it to correctly conduct the
study. Re-running the script generates the study for the next
participant.

\evan{Should I include the python script? It would make explaining how
  the test was conducted 100\% clear.}
